Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-12 emsoft-2019/related.tex
Small change to intro (list of contributions) and added a paper in related work

Any digital controller can be implemented using a wide range of available
platforms. Large-size manufacturers use industrial digital computers called
\emph{programmable logic controller (PLC)} for such implementations. A PLC is
able to perform the computations required by a digital controller using
floating-point arithmetic.  Low-end applications utilize microcontrollers with
limited memory capacity and computational power to keep the costs of the
implementation down.

@@

>>>>

Any digital controller can be implemented using a wide range of available
platforms. Large-size manufacturers use industrial digital computers called
\emph{programmable logic controllers (PLC)} for such implementations. A PLC is
able to perform the computations required by a digital controller using
floating-point arithmetic.  Low-end applications utilize microcontrollers with
limited memory capacity and computational power to keep the costs of the
implementation down.
We target implementations for low-end microcontrollers.

@@

\citet{SahaM12} consider memory optimization for event-driven controllers
using a scratchpad to selectively load control parameters based on the current state.
Our work, in contrast, is a static mapping of controller parameters.
